
# Statistical Inference Assignment - Part A


## Set up steps

### Set up the values for the simulation
```{r}
set.seed(667)
sims <- 1000
n <- 40
lambda <- 0.2
```

### Create a Matrix

```{r}
## create a matrix of a 1000 rows of 40 random exponential values
sim <- matrix(rexp(sims * n, rate = lambda), sims)

```


## 1. This is question number 1

### Take the mean for each row
```{r}
row_means<-rowMeans(sim)
mean(row_means)
```

### Theoretical mean of the sample:

```{r}
1/lambda
```


## 2. This is question number 2

### take the sd of each rowMeans
```{r}
(1/lambda)^2/n
```

### Theoretical sd
```{r}
var(row_means)

```


## 3. This is question number 3

### This histogram visually shows how the ** resembles the **.

```{r}
h<-hist(means, breaks=50, density=20, col="gray", xlab="Accuracy", main="Overall")
    xfit<-seq(min(means),max(means),length=40)
    yfit<-dnorm(xfit,mean=mean(means),sd=sd(means))
    yfit <- yfit*diff(h$mids[1:2])*length(means)
    lines(xfit, yfit, col="blue", lwd=2)
```


# Statistical Inference Assignment - Part B

First load the required libraries
```{r}
library(ggplot2)
library(datasets)
data(ToothGrowth)
```

Here are some basic exploratory data Analyses.
```{r}
str(ToothGrowth)
head(ToothGrowth)
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
table(ToothGrowth$supp, ToothGrowth$dose)
summary(ToothGrowth)
```

A point chart to start visualizing the outcome of the data
```{r}
ggplot(ToothGrowth, aes(x=dose, y=len))+geom_point(color="aquamarine4")+facet_wrap(~supp, nrow=1) +
     labs(x="Dosage", y="Number of Teeth")+  
     ggtitle("Exploratory Data Analyses")

```

We perform a t-test on the data to determine whether our null hypothesis can be rejected.
```{r}

v1 <- t.test(len~supp, paired=F, var.equal=T, data=ToothGrowth)
v2 <- t.test(len~supp, paired=F, var.equal=F, data=ToothGrowth)
Vresults <- data.frame("p-value"=c(v1$p.value, v2$p.value),
                          "Conf-Low"=c(v1$conf[1],v2$conf[1]),
                          "Conf-High"=c(v1$conf[2],v2$conf[2]),
                          row.names=c("Equal Var","Unequal Var"))
Vresults

```
